---
title: "FARS vignette"
author: "Nick Bohl"
date: "November 5, 2018"
output:
  html_document: default
  pdf_document: default
---

# Package Description

This package is intended to allow light analysis of the Fatality Analysis Reporting System (FARS). This package will provide a mapping tool for plotting accident rates of an individual state. The FARS census information is provided by the National Highway Traffic Safety Administration (NHTSA).

# Load the Needed Packages

```{r import libraries}
 library(fars)
 suppressWarnings(library(maps))
```

# Package Functions Summary

Three functions will be accessible to the end-user

 `fars_read()` (accessible to end-user)
 `make_filename()`
 'fars_read_years()'
 `fars_summarize_years()` (accessible to end-user)
 'fars_map_state()` (accessible to end-user)
 

# Summary of Exports

The fars_read() function allows the package to read example datafiles from a predetrmined path location. an output dataframe is generated for the user.

```{r fars_read_example}
example_file <- system.file("extdata/accident_2014.csv.bz2", package = "fars")
fars_read(example_file)
```

```{r fars_summarize_years_example}
setwd(system.file("extdata", package = "fars"))
fars_summarize_years(c(2013))
```

```{r fars_map_state_example}
setwd(system.file("extdata", package = "fars"))
state_num <- 18
fars_map_state(state_num, 2014)

